### 2021-03-09 research project/sections/Conclusion.tex
rp work

>>>>

\subsection{Personal reflection}

This paper has been interesting to write for me. The topic I chose seemed daunting in the beginning, and math was not a favorite subject of mine to say the least. I had to research concepts outside my understanding and the curriculum, and challenge my own programming knowledge. To add to this, I also managed to understand how important time management skills are for these types of tasks. By challenging myself like this, I think I have not only learned to like the field of mathematics but also develop important skills. I have also learned to use new software, notably the typesetting software \LaTeX{} and its bibliography management tool \verb|bibtex|, which proved very useful in the writing of this paper, and facilitated many boring tasks. To finally conclude, I think the skills I have learned through this paper (along with the probably numerous mistakes), will help me understand and organize myself for future projects of the same kind.
